---
title: "Item Analysis Report"
date: '`r Sys.Date()`'
output: 
    html_document:
       number_sections: true
       toc: true
subtitle: |
  This report was generated by ShinyItemAnalysis application version `r packageVersion("ShinyItemAnalysis")`
  
  Copyright 2017 Patricia Martinkova, Adela Drabinova, Ondrej Leder and Jakub Houdek.
  
  Supported by Czech Science Foundation under grant number [GJ15-15856Y](http://www.cs.cas.cz/martinkova/psychometrics.html)
params:
  a: NA
  k: NA
  gr: NA
  results: NA
  histogram_totalscores: NA
  corr_plot: NA
  scree_plot: NA
  difPlot: NA
  hist_distractor_by_group: NA
  graf: NA
  logreg: NA
  zlogreg: NA
  zlogreg_irt: NA
  nlsplot: NA
  multiplot: NA
  wrightMap: NA
  irt: NA
  irtiic: NA
  irttif: NA
  irtcoef: NA
  irtfactor: NA
  resultsgroup: NA
  histbyscoregroup0: NA
  histbyscoregroup1: NA
  deltaplot: NA
  DP_text_normal: NA
  DIF_logistic_print: NA
  DIF_logistic_plot: NA
  plot_DIF_logistic: NA
  plot_DIF_logistic_IRT_Z: NA
  plot_DIF_NLR: NA
  plot_DIF_IRT_Lord: NA
  plot_DIF_IRT_Raju: NA
  itemexam: NA
  itemReport: NA
  irt_type: NA
  model_DDF_print: NA
  plot_DDFReportInput: NA
  isGroupPresent: NA
  dif_type: NA
  groupie: NA
---
\pagebreak

# Summary report

## Summary of total scores

```{r total-scores, echo = FALSE, results = "hide"}
library(gridExtra)
params$irt_report
table = params$results
table = round(table, digits = 4)
colnames(table) = NULL
table = tableGrob(t(table))
hist = ggplotGrob(params$histogram_totalscores)
lay = rbind(c(1, 1, 1),
            c(2, 2, 2),
            c(2, 2, 2),
            c(2, 2, 2),
            c(2, 2, 2))
grid.arrange(table, hist, ncol = 1, top = "Basic summary and histogram", layout_matrix = lay)
```

**`r if (params$corr_plot != "") {"## Correlation structure"}`**

```{r corr-plot, echo = FALSE, fig.height = 4}
if (params$corr_plot != "") {
  corrplot(params$corr_plot)
}
```

```{r scree-plot, echo = FALSE, fig.height = 4}
if (params$corr_plot != "") {
  params$scree_plot + ggtitle("Scree plot")
}
```


\pagebreak


# Traditional item analysis report

## Item analysis

```{r DD-plot, echo = FALSE, results = "hide"}
params$difPlot
```

```{r item-table, echo = FALSE}
table = params$itemexam
tab = format(round(table[, -1], 4), nsmall = 3)
table = data.frame(table[, 1], tab)
colnames(table) = c("Item", "Diff.", "SD", "D. ULI", "D. RIT", "D. RIR", "Alpha Drop")
rownames(table) = NULL
table
```

## Distractor analysis

```{r distractor-multi-plot, echo = FALSE, results = "hide", fig.width = 10}
for (i in 1:length(params$graf)){
  grid.arrange(params$graf[[i]], params$multiplot[[i]], ncol = 2)
}
```


\pagebreak

#IRT model

```{r irt-eq, echo = FALSE, results = "hide"}
if (params$irt_type == "rasch") {
  head = " Rasch model"
}

if (params$irt_type == "1pl") {
head = " 1PL IRT model"
eq = "$ {P}(Y_{ij} = 1|\theta_{i},a,b_j) =\frac{e^{a(\theta_i-b_j)}}{1+e^{a(\theta_i-b_j)}} $"
}

if (params$irt_type == "2pl") {
head = " 2PL IRT model"
eq = "$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j) = \frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$"
}

if (params$irt_type == "3pl") {
head = " 3PL IRT model"
#eq = "$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j, c_j) = c_j + (1+c_j)\cdot\frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$"
}

if (params$irt_type == "none") {
head = " None"
}
```



Available models:

Rasch model
$$ {P}(Y_{ij} = 1|\theta_{i},b_j) =\frac{e^{(\theta_i-b_j)}}{1+e^{(\theta_i-b_j)}} $$

1PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a,b_j) =\frac{e^{a(\theta_i-b_j)}}{1+e^{a(\theta_i-b_j)}}$$

2PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j) = \frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$

3PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j, c_j) =c_j + (1+c_j)\cdot\frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$

**`r if (params$wrightMap!="") {"Wright (item-person) map using 1PL IRT model"}`**

```{r wright-map, echo = FALSE, results = "hide", fig.height = 5, fig.width = 10}
if (params$wrightMap != "") {
  wrightMap(params$wrightMap[[1]], params$wrightMap[[2]], item.side = itemClassic)
}
```

\pagebreak

**Selected model:`r head`**

```{r irt-1, echo = FALSE, results = "hide", fig.height = 4}
params$irt
params$irtiic
```

\pagebreak

```{r irt-2, echo = FALSE, results = "hide", fig.height = 4}
params$irttif
params$irtfactor
```

```{r irt-estim, echo = FALSE, fig.height = 6}
if (params$irt_type != "none") {
  table = params$irtcoef
  table = round(table, 5)
  grid.arrange(tableGrob(table), top = "Parameter estimates and item fit")
}
```

\pagebreak

# DIF/Fairness report

`r if(!params$isGroupPresent){"Group vector is not present. DIF and DDF report could not be generated!"}`

`r if(params$isGroupPresent) {"## Total scores"}`

```{r table-by-group, echo = FALSE}
if(params$isGroupPresent){
params$resultsgroup
}
```

```{r hist-by-group, echo = FALSE, results = "hide"}
if(params$isGroupPresent){
g1 = params$histbyscoregroup0
g2 = params$histbyscoregroup1
grid.arrange(g1, g2, ncol = 1)
}
```

`r if(params$isGroupPresent & params$dif_type>=1) {"## DIF detection using delta plot"}`

```{r delta-plot, echo = FALSE, results = "hide"}
if (params$dif_type >= 1) {
  if(params$isGroupPresent){
  params$deltaplot
  }
}
```

```{r delta-plot-output, echo = FALSE}
if (params$dif_type >= 1) {
  if(params$isGroupPresent){
  params$DP_text_normal
  }
}
```

`r if(params$isGroupPresent & params$dif_type>=2) {"## DIF detection using logistic regression"}`

```{r dif-logistic-output, echo = FALSE}
if (params$dif_type >= 2) {
 if(params$isGroupPresent){
  params$DIF_logistic_print
  } 
}
```

```{r dif-logistic-plot, echo = FALSE, results = 'hide', fig.height = 4.2}
if (params$dif_type >= 2) {
  if(params$isGroupPresent){
  params$DIF_logistic_plot
  }
}
```

`r if(params$isGroupPresent & params$dif_type>=2) {"## DDF detection using multinomial regression"}`

```{r ddf-multi-output, echo = FALSE}
if (params$dif_type >= 3) {
  if(params$isGroupPresent){
  print(params$model_DDF_print)
  }
}
```

```{r ddf-multi-plot, echo = FALSE, results = 'hide', fig.height = 4.2}
if (params$dif_type >= 3) {
  if(params$isGroupPresent){
  params$plot_DDFReportInput
  }
}
```

\pagebreak

# Session Info

```{r echo=FALSE}
sessionInfo()
```

\pagebreak
