---
title: |
  <b>Test and Item Analysis Report</b>
  
  **************
  
output:
    html_document:
       number_sections: false
       toc: true
author: |
  This report was created `r ifelse(params$author == "", "", paste("by", params$author))` `r ifelse(params$dataset == "", "", paste("on", params$dataset, "dataset"))` on `r Sys.Date()`

  ShinyItemAnalysis: Test and item analysis, version `r packageVersion("ShinyItemAnalysis")`

  &copy; 2018 Patricia Martinkova, Adela Drabinova, Ondrej Leder and Jakub Houdek.
    
  **************
  
params:
  customize: NA
  author: NA
  dataset: NA
  totalscores_table: NA
  totalscores_histogram: NA
  totalscores_histogram_cutscore: NA
  totalscores_histogram_text: NA
  standardscores_table: NA
  standardscores_table_text: NA
  corrplot: NA
  corrplot_numclust: NA
  corrplot_methodclust: NA
  corrplot_text: NA
  screeplot: NA
  screeplot_text: NA
  predictivevalidity_plot: NA
  predictivevalidity_plot_text: NA
  DDplot: NA
  DDplot_numgroups: NA
  DDplot_range: NA
  DDplot_text: NA
  DDtable: NA
  DDtable_text: NA
  distractor_plots: NA
  distractor_plots_type: NA
  distractor_plots_numgroups: NA
  distractor_plots_text: NA
  irt: NA
  irt_model: NA
  irt_equation: NA
  irt_text: NA
  irt_wrightmap: NA
  irt_wrightmap_text: NA
  irt_table: NA
  irt_table_text: NA
  dif_histograms: NA
  dif_histograms_cutscore: NA
  dif_histograms_text: NA
  dif_deltaplot: NA
  dif_deltaplot_threshold: NA
  dif_deltaplot_purification: NA
  dif_deltaplot_purification_type: NA
  dif_deltaplot_text: NA
  dif_logistic: NA
  dif_logistic_type: NA
  dif_logistic_correctionmethod: NA
  dif_logistic_purification: NA
  dif_logistic_text: NA
  dif_logistic_plot_text: NA
  dif_multinomial: NA
  dif_multinomial_type: NA
  dif_multinomial_correctionmethod: NA
  dif_multinomial_purification: NA
  dif_multinomial_text: NA
  dif_multinomial_plot_text: NA
---

**************

# Introduction

This report provides test and item analysis using ShinyItemAnalysis version `r packageVersion("ShinyItemAnalysis")`. ShinyItemAnalysis is available on
[CRAN](https://CRAN.R-project.org/package=ShinyItemAnalysis) and also [online](https://shiny.cs.cas.cz/ShinyItemAnalysis/). This project is supported by Czech Science Foundation under grant number [GJ15-15856Y](http://www.cs.cas.cz/martinkova/psychometrics.html).

**************

# Summary

## Total scores

**Summary table of total scores**

```{r total-scores-table, echo = FALSE}
library(knitr)
table = params$results
colnames(table) = NULL

kable(t(table), digits = c(0, 0, 3, 0, 3, 3, 3), align = 'c')
```

For selected cut-score, blue part of histogram shows students with total score above the cut-score, grey column shows students with total score equal to the cut-score and red part of histogram shows students below the cut-score.

```{r total-scores-histogram, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
params$histogram_totalscores + 
  ggtitle('Histogram of total scores') + 
  theme(text = element_text(size = 10), 
        plot.title = element_text(face = "bold"))
```

**************

# Scoring

**Summary table of standard scores**: Total score also known as raw score is a total number of correct answers. It can be used to compare individual score to a norm group, e.g. if the mean is 12, then individual score can be compared to see if it is below or above this average. Percentile indicates the value below which a percentage of observations falls, e.g. a individual score at the 80th percentile means that the individual score is the same or higher than the scores of 80% of all respondents. 
Success rate is the percentage of success, e.g. if the maximum points of test is equal to 20 and individual score is 12 then success rate is 12/20 = 0.6, i.e. 60%. 
Z-score or also standardized score is a linear transformation of total score with a mean of 0 and with variance of 1. If X is total score, M its mean and SD its standard deviation then Z-score = (X - M) / SD. T-score is transformed Z-score with a mean of 50 and standard deviation of 10. If Z is Z-score then T-score = (Z * 10) + 50.

```{r standard-scores-table, echo = FALSE}
table = params$standardscores_table
kable(table, align = 'c')
```

`r if (any(params$corr_plot != "") | params$validity_check) {"**************"}`

`r if (any(params$corr_plot != "") | params$validity_check) {"# Validity"}`

`r if (any(params$corr_plot != "")) {"## Correlation structure"}`

`r if (any(params$corr_plot != "")) {"**Polychoric correlation heat map** is a correlation plot which displays a polychoric correlations of items. The size and shade of circles indicate how much the items are correlated (larger and darker circle means larger correlation). The color of circles indicates in which way the items are correlated - blue color shows possitive correlation and red color shows negative correlation."}`

`r clustmethod_names <- c("None" = "none",
                          "Ward's"  = "ward.D",
                          "Ward's n. 2" = "ward.D2",
                          "single" = "single",
                          "complete" = "complete",
                          "average" = "average",
                          "McQuitty" = "mcquitty",
                          "median" = "median",
                          "centroid" = "centroid")`
`r if (any(params$corr_plot != "") & params$corr_plot_clustmethod != "none") {paste("Polychoric correlation heat map is reorder using hierarchical clustering with", names(clustmethod_names)[clustmethod_names == params$corr_plot_clustmethod], "linkage method. Number of", params$corr_plot_numclust, "clusters is considered. ")}`

```{r corr-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (any(params$corr_plot != "")) {
  corP <- params$corr_plot
  numclust <- params$corr_plot_numclust
  clustmethod <- params$corr_plot_clustmethod
  
  tlcex <- 0.7
  
  if (clustmethod == "none"){
    corrplot(corP, tl.cex = )
  } else {
    corrplot(corP, tl.cex = tlcex, order = "hclust", 
             hclust.method = clustmethod, addrect = numclust)
  }
}
```

`r if (any(params$corr_plot != "")) {"**Scree plot** displays the eigenvalues associated with an component or a factor in descending order versus the number of the component or factor."}`

```{r scree-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (any(params$corr_plot != "")) {
  params$scree_plot + 
    ggtitle("Scree plot") + 
    theme(text = element_text(size = 10), 
          plot.title = element_text(face = "bold"))
}
```

`r if (params$validity_check) {"## Predictive validity"}`

`r if(!(params$isCriterionPresent) & params$validity_check){"Criterion variable vector is not present. Predictive validity analysis could not have been generated!"}`

```{r validity-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if(params$isCriterionPresent & params$validity_check){
  params$validity_plot + 
    theme(text = element_text(size = 10))
}
```

```{r validity-table, echo = FALSE, results = 'hide'}
if(params$isCriterionPresent & params$validity_check){
  tab <- params$validity_table
  p.val <- tab["p-value"]
  rho <- tab[1]

  txt1 <- ifelse(p.val < 0.05, "less than", "larger than")
  txt2 <- ifelse(p.val < 0.05, "reject", "do not reject")
  txt3 <- ifelse(p.val < 0.05, 
                 paste("total score and criterion variable are", ifelse(rho > 0, "positively", "negatively"), "correlated."),
                 paste("we cannot conclude that a significant correlation between total score
                        and criterion variable exists."))
  txt4 <- paste("Test for association between total score and criterion variable is based on Spearman`s ", expression(rho), 
                ". The null hypothesis is that correlation is 0. ", sep = "") 
  txt5 <- paste("Results: ", expression(rho), " = ", rho, " (p-value ", p.val ,").", sep = "") 
  txt6 <- paste("Interpretation: The p-value is", txt1, "0.05, thus we", txt2, "the null hypothesis;", txt3)
  
  txt <- paste(txt4, txt5, txt6, collapse = "/n")
}

```

`r if(params$isCriterionPresent & params$validity_check){txt}`

**************

# Traditional item analysis

## Item analysis

Difficulty (red) of items is estimated as percent of students who answered correctly to that item. Discrimination (blue) is by default described by difference of percent correct in upper and lower third of students (Upper-Lower Index, ULI). By rule of thumb it should not be lower than 0.2 (borderline in the plot), except for very easy or very difficult items.

```{r DD-plot-interpretation, echo = FALSE, results = "hide"}
range1 <- params$DDplotRange1
range2 <- params$DDplotRange2
numgroups <- params$DDplotNumGroups

  if (any(range1 != 1, range2 != 3, numgroups != 3)) {
    DDplot_interpretation=HTML(paste(
      "Discrimination is here a difference between the difficulty recorded in the ",
      "<b>", range1, "</b>",
      ifelse(range1 >= 4, "-th", switch(range1, "1" = "-st", "2" = "-nd", "3" = "-rd")),
      " and <b>", range2, "</b>",
      ifelse(range2 >= 4, "-th", switch(range2, "1" = "-st", "2" = "-nd", "3" = "-rd")),
      " group out of total number of ",
      "<b>", numgroups, "</b>",
      " groups. <br><br>",
      sep = ""
    ))
  }
```

`r if (any(range1 != 1, range2 != 3, numgroups != 3)) {DDplot_interpretation}`

<!-- THIS HAS TO BE MODIFY - ADD INFO WHAT GROUPS WERE SELECTED -->
```{r DD-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
params$difPlot + 
  ggtitle('Difficulty/Discrimination plot') + 
  theme(text = element_text(size = 10), 
        plot.title = element_text(face = "bold"))
```

**Traditional item analysis table**: Diff. - Difficulty of item is estimated as percent of students who answered correctly to that item. SD - standard deviation, ULI - Upper-Lower Index, RIT - Pearson correlation between item and total score, RIR - Pearson correlation between item and rest of items, Alpha Drop - Cronbach's alpha of test without given item, Cust. D.- difference between the difficulty recorded in the groups selected by user.

```{r item-table, echo = FALSE}
table = params$itemexam
tab = format(round(table[, -1], 4), nsmall = 3)
table = data.frame(table[, 1], tab)
colnames(table) = c("Item", "Diff.", "SD", "D. ULI", "D. RIT", "D. RIR", "Alpha Drop", "Cust. D.")
rownames(table) = NULL

kable(table, digits = c(0, 4, 4, 4, 4, 4, 4), align = 'c')
```

## Distractor analysis

Respondents are divided into selected number groups by their total score. Subsequently, the percentage of students in each group who selected given answer (correct answer or distractor) is displayed. The correct answer should be more often selected by strong students than by students with lower total score, i.e. solid line should be increasing. The distractor should work in opposite direction, i.e. dotted lines should be decreasing.

```{r distractor-multi-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
library(gridExtra)
for (i in 1:length(params$graf)){
  g1 <- params$graf[[i]]
  g2 <- params$multiplot[[i]]
  grid.arrange(g1, g2, ncol = 2)
}
```

**************

# IRT models

Item Response Theory (IRT) models are mixed-effect regression models in which student ability (theta) is assumed to be a random effect and is estimated together with item paramters. Ability (theta) is often assumed to follow normal distibution.

```{r irt-eq, echo = FALSE, results = "hide"}
if (params$irt_type == "rasch") {
  head = " Rasch model"
}

if (params$irt_type == "1pl") {
head = " 1PL IRT model"
eq = "$ {P}(Y_{ij} = 1|\theta_{i},a,b_j) =\frac{e^{a(\theta_i-b_j)}}{1+e^{a(\theta_i-b_j)}} $"
}

if (params$irt_type == "2pl") {
head = " 2PL IRT model"
eq = "$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j) = \frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$"
}

if (params$irt_type == "3pl") {
head = " 3PL IRT model"
#eq = "$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j, c_j) = c_j + (1+c_j)\cdot\frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$"
}

if (params$irt_type == "none") {
head = " None"
}
```

Available models:

Rasch model
$$ {P}(Y_{ij} = 1|\theta_{i},b_j) =\frac{e^{(\theta_i-b_j)}}{1+e^{(\theta_i-b_j)}} $$

1PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a,b_j) =\frac{e^{a(\theta_i-b_j)}}{1+e^{a(\theta_i-b_j)}}$$

2PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j) = \frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$

3PL IRT model
$$ {P}(Y_{ij} = 1|\theta_{i},a_j,b_j, c_j) =c_j + (1+c_j)\cdot\frac{e^{a_j(\theta_i-b_j)}}{1+e^{a_j(\theta_i-b_j)}}$$

**`r if (any(params$wrightMap!="")) {"Wright (item-person) map using 1PL IRT model"}`**

`r if (any(params$wrightMap!="")) {"Wright map, also called item-person map, is a graphical tool to display person estimates and item parameters. The person side (left) represents histogram of estimated knowledge of students. The item side (right) displays estimates of difficulty of particular items."}`


```{r wright-map, echo = FALSE, results = "hide", fig.height = 5.5, fig.width = 11, fig.align = 'center'}
if (any(params$wrightMap != "")) {
  wrightMap(params$wrightMap[[1]], params$wrightMap[[2]], item.side = itemClassic)
}
```


**Selected model:`r head`**

```{r irt-0, echo = FALSE, results = "hide", fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (params$irt_type != "none") {
  params$irt
}
```

```{r irt-1, echo = FALSE, results = "hide", fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (params$irt_type != "none") {
  params$irtiic
}
```

```{r irt-2, echo = FALSE, results = "hide", fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (params$irt_type != "none") {
  params$irttif
}
```

**`r if (params$irt_type != "none") {"Parameter estimates and item fit"}`**

`r if (params$irt_type != "none") {"Estimates of parameters are completed by SX2 item fit statistics. SX2 is computed only when no missing data are present. In such a case consider using imputed dataset!"}`

```{r irt-estim, echo = FALSE}
if (params$irt_type != "none") {
  table = params$irtcoef
  # table = round(table, 5)
  
  kable(table, align = 'c')
}
```

**`r if (params$irt_type != "none") {"Ability estimates"}`**

```{r irt-3, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center', dpi = 300}
if (params$irt_type != "none") {
  params$irtfactor + 
    ggtitle('Scatterplot of factor scores and standardized total scores') + 
    theme(text = element_text(size = 10), 
          plot.title = element_text(face = "bold"))
}
```

`r if (any(c(params$histCheck, params$deltaplotCheck, params$logregCheck, params$multiCheck)) & params$isGroupPresent) {"**************"}`


`r if(any(c(params$histCheck, params$deltaplotCheck, params$logregCheck, params$multiCheck))) {"# DIF/Fairness analysis"}`

`r if(any(c(params$histCheck, params$deltaplotCheck, params$logregCheck, params$multiCheck)) & !params$isGroupPresent){"Group vector is not present. DIF and DDF analyses could have not been generated!"}`

`r if(params$isGroupPresent & params$histCheck) {"## Total scores by group"}`

`r if(params$isGroupPresent & params$histCheck) {"**Summary table of total scores in reference and focal group**"}`

`r if(params$isGroupPresent & params$histCheck) {"DIF is not about total scores! Two groups may have the same distribution of total scores, yet, some item may function differently for two groups. Also, one of the groups may have signifficantly lower total score, yet, it may happen that there is no DIF item!"}`

```{r table-by-group, echo = FALSE}
if (params$histCheck) {
  if(params$isGroupPresent){
    kable(params$resultsgroup, digits = c(0, 0, 3, 0, 3, 3, 3), align = 'c')
  }
}
```


```{r hist-by-group, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center'}
if (params$histCheck) {
  if(params$isGroupPresent){
    g1 = params$histbyscoregroup0 + 
      theme(text = element_text(size = 10), 
            plot.title = element_text(face = "bold"))
    g2 = params$histbyscoregroup1 + 
      theme(text = element_text(size = 10), 
            plot.title = element_text(face = "bold"))
    grid.arrange(g1, g2, nrow = 1)
  }
}
```

`r if(params$isGroupPresent & params$deltaplotCheck) {"## Delta plot"}`

`r if(params$isGroupPresent & params$deltaplotCheck) {"Delta plot compares the proportions of correct answers per item in the two groups. It displays non-linear transformation of these proportions using quantiles of standard normal distributions (so called delta scores) for each item for the two groups in a scatterplot called diagonal plot or delta plot . Item is under suspicion of DIF if the delta point considerably departs from the diagonal. "}`

```{r delta-plot-output, echo = FALSE}
if (params$deltaplotCheck) {
  if(params$isGroupPresent){
    params$DP_text_normal
  }
}
```


```{r delta-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center'}
if (params$deltaplotCheck) {
  if(params$isGroupPresent){
    print(params$deltaplot +
            geom_text(size = 0.1) +
            theme(text = element_text(size = 10), 
                  plot.title = element_text(face = "bold")))
  }
}
```

`r if(params$isGroupPresent & params$logregCheck) {"## DIF detection using logistic regression"}`

`r if(params$isGroupPresent & params$logregCheck) {"Logistic regression allows for detection of uniform and non-uniform DIF by adding a group specific intercept (uniform DIF) and group specific interaction (non-uniform DIF) into model and by testing for their significance."}`

```{r dif-logistic-output, echo = FALSE}
if (params$logregCheck) {
 if(params$isGroupPresent){
  params$DIF_logistic_print
  } 
}
```

`r if(params$isGroupPresent & params$logregCheck) {"Plots and tables are based on DIF logistic procedure without any correction method."}`

```{r dif-logistic-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center'}
if (params$logregCheck) {
  if(params$isGroupPresent){
    for (i in 1:length(params$DIF_logistic_print$DIFitems)){
      print(params$DIF_logistic_plot[[i]] + 
              theme(text = element_text(size = 10), 
                    plot.title = element_text(size = 12, face = "bold")))
    }
  }
}
```

`r if(params$isGroupPresent & params$multiCheck) {"## DDF detection using multinomial regression"}`

`r if(params$isGroupPresent & params$multiCheck) {"Differential Distractor Functioning (DDF) occurs when people from different groups but with the same knowledge have different probability of selecting at least one distractor choice. DDF is here examined by multinomial log-linear regression model with Z-score and group membership as covariates. "}`

```{r ddf-multi-output, echo = FALSE}
if (params$multiCheck) {
  if(params$isGroupPresent){
    print(params$model_DDF_print) 
  }
}
```

`r if(params$isGroupPresent & params$multiCheck) {"Points represent proportion of selected answer with respect to standardized total score. Size of points is determined by count of respondents who chose particular answer. "}`

```{r ddf-multi-plot, echo = FALSE, fig.width = 11, fig.height = 4, fig.align = 'center'}
if (params$multiCheck) {
  if(params$isGroupPresent){
    for (i in 1:length(params$model_DDF_print$DDFitems)){
      print(params$plot_DDFReportInput[[i]] + 
              theme(text = element_text(size = 14), 
                    plot.title = element_text(size = 16, face = "bold")))
    }
  }
}
```


**************

# Session info

```{r session-info, echo = FALSE}
sessionInfo()
```

\pagebreak
